---
title: "Mock Paper"
subtitle: "A reproducible manuscript written in Quarto."
format: 
  html:
    toc: true
    code-tools: true
execute:
  warning: false
  error: false
bibliography: references.bib
---

## Introduction

What did the fox say. What did the fox say. What did the fox say. What did the fox say. What did the fox say. What did the fox say. What did the fox say. What did the fox say. What did the fox say.

## Data

```{r}

## Dependencies
library(tidyverse)
library(reactable) ## Interactive tables
library(highcharter) ## Interactive viz
library(sjPlot) ## Model sumamry
library(lme4) ## Mixed models

## Figure 1 Data
data_fig1 =  data.frame(
    stringsAsFactors = FALSE,
    name = c(
      "The Left",
      "Social Democratic Party",
      "Alliance 90/The Greens",
      "Free Democratic Party",
      "Christian Democratic Union",
      "Christian Social Union in Bavaria",
      "Alternative for Germany"
    ),
    count = c(69, 153, 67, 80, 200, 46, 94),
    col = c("#BE3075", "#EB001F", "#64A12D", "#FFED00",
            "#000000", "#008AC5", "#009EE0"
    ),
    abbrv = c("DIE LINKE", "SPD", "GR???NE", "FDP", "CDU", "CSU", "AfD")
  )

## Figure 2 Data
data(GNI2014, package = "treemap")
data_fig2 = GNI2014  


## Figure 3 Data
data("sleepstudy")
data("efc")
efc$cluster <- as.factor(efc$e15relat)
```

For this paper we will be using some dummy data. The libraries and data simulation or imports are shown above.

## Methods

```{r}
m1 <- lmer(neg_c_7 ~ c160age + c161sex + e42dep + (1 | cluster), data = efc)
m2 <- lmer(Reaction ~ Days + (1 + Days | Subject), data = sleepstudy)
```

We fit the following model. We specificied age as What did the fox say.

$$
y = x_1\beta_1 + x_2\beta_2 + x_2^2\beta_3 + \varepsilon
$$ {#eq-model}


## Foxes are not green

What did the fox say. What did the fox say. What did the fox say. What did the fox say. What did the fox say. What did the fox say. What did the fox say. What did the fox say. What did the fox say.

```{r}
#| label: fig-plot
#| fig-cap: "The distribution of something for something."

hchart(
  data_fig1,
  "item",
  hcaes(
    name = name,
    y = count,
    label = abbrv,
    color = col
  ),
  name = "Representatives",
  showInLegend = TRUE,
  size = "100%",
  center = list("50%", "75%"),
  startAngle = -100,
  endAngle  = 100
)  
```

## Foxes like maps

What did the fox say. What did the fox say. What did the fox say. What did the fox say. What did the fox say. What did the fox say. What did the fox say. What did the fox say. What did the fox say.

```{r}
#| label: fig-map
#| fig-cap: "Foxes realy like maps but are hard to find."

hcmap(
    "custom/world-robinson-lowres",
    data = GNI2014,
    name = "Gross national income per capita",
    value = "GNI",
    borderWidth = 0,
    nullColor = "#d3d3d3",
    joinBy = c("iso-a3", "iso3")
  ) |>
    hc_colorAxis(
      stops = color_stops(colors = viridisLite::inferno(10, begin = 0.1)),
      type = "logarithmic"
    )
```

## Model

What did the fox say. What did the fox say. What did the fox say. What did the fox say. What did the fox say. What did the fox say. What did the fox say. What did the fox say. What did the fox say.

```{r}
#| label: tbl-map
#| tbl-cap: "Foxes realy like maps but are hard to find."

tab_model(m1, m2)
```

## Discussion

Foxes are cute @Fox2020. We also show this in @fig-plot. However our modeling reports that tail length significantly affects cuteness, see @tbl-map. What did the fox say. What did the fox say. What did the fox say. What did the fox say. What did the fox say. What did the fox say. What did the fox say. What did the fox say. What did the fox say.
